### 2022-05-09 supplement.Rmd
Bias correction also for gender

```{r, trim_and_fill}

@@

```{r,selection_models}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

@@

```{r, tabs_trimfill_selectionmodels, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model:severe two-tailed",
  "Selection model: weight-function [0.01,0.05,0.3]"),
    list(
      r_mod,
      res_tf,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed,
      sel_mod),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

@@

>>>>

```{r, trim_and_fill_within}

@@

```{r,selection_models_within}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

@@

```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

@@

```{r, trim_and_fill_gender}
dat=dat_gender

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

```{r,selection_models_gender}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
```
